resistanceModelNotesAndy

### 2015-03-20 resistanceModelNotesAndy.Rmd
progress notes

**16/3/15** mon 18.30-19.30 1hr

cut out lines 92 to 1740 into a runModel() function, later can subdivide it up

In max(combmat[, gencol]) : no non-missing arguments to max; returning -Inf
fixed by returning listOut from runModel()

@@

done: add a savePlots argument, to enable plotting without saving

@@

~60,000 combinations…. Too many???

@@

These ratios was then analysed by regression to find out how the input parameters alter the ratio, and hence under what circumstance combination would be best/worst. Classification tress can also be done….

@@

### TO DO  
1. add myself as maintainer in DESCRIPTION
1. sort licence in description
1. put back in checks for things that should sum to 1
1. edit runModel carefully
1. check whether functions can run without "input.parameters.csv" 
1. check out the part about running sequential insecticide scenarios
1. start to write script to run sensitivity analysis, does it want to work by creating a large input.csv file, or by setting input object directly.
1. spend some time developing my understanding of how the model works
1. submit tilde bug report
1. later, structure as R package, maybe move to a new github repo
1. re-look at R popgen packages when I've got more of a handle on what we are doing.

### suggestion from Beth
looking at it now I realise this is not ideal
a solution may be to provide a .csv file with the Curtis scenarios set up
and then the need to set the calibration number and params.csv in the R script can be removed altogether
so it is all set up in the .csv file - I think similar can be done with produce.plots
so the only bit of R code the user will need to change is the setwd() and the read.csv()

>>>>

**16/3/15** mon 18.30-19.30 1hr
cut out lines 92 to 1740 into a runModel() function, later can subdivide it up

@@

@@

Approx. 60,000 combinations. Too many???

@@

These ratios was then analysed by regression to find out how the input parameters alter the ratio, and hence under what circumstance combination would be best/worst. Classification tress can also be done.

@@

**19/3/15** fri 9.45-14 4.25hrs 3.30-7 3.5hrs 7.75hrs

checking whether I can run without the input file. Fixed now.

```{r}
resistanceMaster(params.csv = FALSE)
```

This is what the fitness scores that can be saved for each scenario as *two-locus_fitness-scores.csv look like :
```
	-,-	a,-	A,-	-,b	-,B	a,b	A,B	A,b	a,B
SS1SS2	1	0	0	0	0	0	0	0	0
SS1RS2	1	0	0	0	0	0	1.86E-05	0	0
SS1RR2	1	0	0	0	0	0	0.1161	0	0
RS1SS2	1	0	0	0	0	0	0	0	0
RS1RS2	1	0	0	0	0	0	2.13E-05	0	0
RS1RR2	1	0	0	0	0	0	0.132913	0	0
RR1SS2	1	0	0	0	0	0	0	0	0
RR1RS2	1	0	0	0	0	0	3.44E-05	0	0
RR1RR2	1	0	0	0	0	0	0.215	0	0
```

Starting resistSimple() to be able to run single simpleScenarios.

### TO DO

1. check whether setting input[13,1] <- to the next line at 58 in createInputMatrix() was a bug

1. finish tidying documentation of reading in input vars in createInputMatrix() add avr names from runModel()
+ can use these later for roxygen doc of function inputs to resistSimple
+ and I could use find&replace to rename later if needed

1. sort that resistSimple will only work with calibration of 1012

1. make it easier to run a single scenario and default scenarios
+ might do this by first adding a function rather than changing existing stuff
1. i think the main visual output is the frequency of resistance over time
1. start creating a vignette to help me understand how the model works

1. the curtis fig2 plot is produced from >1 scenario, do I want to get it into 1 'reactive' scenario
1. put back in checks for things that should sum to 1
1. edit runModel carefully
1. check out the part about running sequential insecticide scenarios
1. start to write script to run sensitivity analysis, does it want to work by creating a large input.csv file, or by setting input object directly.
1. spend some time developing my understanding of how the model works
1. submit tilde bug report
1. later, structure as R package, maybe move to a new github repo
1. re-look at R popgen packages when I've got more of a handle on what we are doing.

### suggestion from Beth
a solution may be to provide a .csv file with the Curtis scenarios set up
and then the need to set the calibration number and params.csv in the R script can be removed altogether
the only bit of R code the user will need to change is the setwd() and the read.csv()

### variable naming conventions
**SS1, RS1, RR1** homozygous susceptible, heterozygous or homozygous resistant genotypes at each locus.   
With 2 loci there are ten possible genotypes (including cis & trans forms of the double heterozygous).

** A, B, a, b, -** 2 insecticides at 3 levels; low(ab), high(AB), absent(--) resulting in 9 niches.

Locus1 relates to resistance for insecticide A, and locus2 for B. Locus2 does not effect exposure to A.

```
colnames(fitness) <- c( "-,-", "a,-", "A,-", "b,-", "B,-", "a,b", "A,B", "A,b", "a,B" )
rownames(fitness) <- c( "SS1SS2", "SS2RS2", "SS1RR2", 
                        "RS1SS2", "RS1RS2_cis", "RS1RS2_trans", "RS1RR2",
                        "RR1SS2", "RR1RS2", "RR1RR2")
```
